When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases

### 2018-02-14 paper/paper.tex
Most (review 2)

\begin{abstract}
    The subgraph isomorphism problem involves finding a copy of a pattern graph inside a larger
    target graph. The non-induced version allows extra edges in the target, whilst the induced
    version does not.  Although both variants are \NP-complete, algorithms inspired by constraint programming
    can operate comfortably on most real-world graphs with thousands of vertices.  However, they
    cannot handle arbitrary instances of this size. We show how to generate ``really hard'' random
    instances for subgraph isomorphism problems, which are computationally challenging with a couple
    of hundred vertices in the target, and only twenty pattern vertices. For the non-induced version
    of the problem, these instances lie on a satisfiable / unsatisfiable phase transition, whose
    location we can predict; for the induced variant, much richer behaviour is observed, and
    constrainedness gives a better measure of difficulty than does proximity to a phase transition.
    These results have practical consequences: we explain why the widely researched ``filter~/
    verify'' indexing technique used in graph databases is founded upon a
    misunderstanding of the empirical hardness of \NP-complete problems, and cannot be beneficial
    when paired with any reasonable subgraph isomorphism algorithm.
\end{abstract}

>>>>

\begin{abstract}
    The subgraph isomorphism problem involves finding a copy of a pattern graph inside a larger
    target graph. The non-induced version allows extra edges in the target, whilst the induced
    version does not.  Although both variants are \NP-complete, algorithms inspired by constraint programming
    can operate comfortably on many real-world problem instances with thousands of vertices.
    However, they cannot handle arbitrary instances of this size. We show how to generate ``really
    hard'' random instances for subgraph isomorphism problems, which are computationally challenging
    with a couple of hundred vertices in the target, and only twenty pattern vertices. For the
    non-induced version of the problem, these instances lie on a satisfiable / unsatisfiable phase
    transition, whose location we can predict; for the induced variant, much richer behaviour is
    observed, and constrainedness gives a better measure of difficulty than does proximity to a
    phase transition.  These results have practical consequences: we explain why the widely
    researched ``filter~/ verify'' indexing technique used in graph databases is founded upon a
    misunderstanding of the empirical hardness of \NP-complete problems, and cannot be beneficial
    when paired with any reasonable subgraph isomorphism algorithm.
\end{abstract}
